Model Estimation

### 2018-12-10 model_estimation.Rmd
WIP

access_sdm_val <- optim(
  fn = notweets_logsum,  
  par = c(-1, 2), # distance, size 
  lower = c(-100, 0), # size coefficient must be positive 
  upper = c(0, 100), # distance coefficient must be negative 
  distances = log(distances), parks = parks, tracts = tracts, 
  model = obese_base_sdm, 
  method = "L-BFGS-B", 
  control = list(fnscale = -1, trace = 6))
```

@@

  logsum <- calculate_park_logsums(
    d = distances,  sizes = parks$log_size, tweets = parks$log_tweets,
    betas = betas)

@@

tweets_sdm_val <- optim(
  fn = notweets_logsum,  
  par = c(-1, 1, 0),
  lower = c(-100, 0, -100), # size coefficient must be positive
  upper = c(0, 100, 100), # distance coefficient must be negative
  hessian=TRUE, distances = distances, parks = parks, tracts = tracts, 
  model = obese_base_sdm, 
  method = "L-BFGS-B", 
  control = list(fnscale = -1, trace = 6))

@@

```{r obesity_access_models}
tracts@data <- tracts@data %>%
  mutate(
    access_ls = calculate_park_logsums(log(distances), parks$log_size,
                                       betas = access_sdm_val$par),
    tweets_ls = calculate_park_logsums(log(distances), parks$log_size, parks$log_tweets,
                                       betas = tweets_sdm_val$par),
    # demean
    access_ls = access_ls - mean(access_ls),
    tweets_ls = tweets_ls - mean(tweets_ls)
  )

>>>>

access_sdm_val <- optim(
  fn = notweets_logsum,  
  par = c(-1, 2), # distance, size 
  lower = c(-100, 0), # size coefficient must be positive 
  upper = c(0, 100), # distance coefficient must be negative 
  distances = distances, parks = parks, tracts = tracts, 
  model = obese_base_lm, 
  method = "L-BFGS-B", 
  control = list(fnscale = -1, trace = 6))
```

@@

  logsum <- calculate_park_logsums(
    d = distances,  sizes = parks$Park_Acres, tweets = parks$TWEET_COUNT,
    betas = betas)

@@

tweets_sdm_val <- optim(
  fn = notweets_logsum,  
  par = c(access_sdm_val$par, 0),
  lower = c(-100, 0, -100), # size coefficient must be positive
  upper = c(0, 100, 100), # distance coefficient must be negative
  hessian=TRUE, distances = distances, parks = parks, tracts = tracts, 
  model = obese_base_sdm, 
  method = "L-BFGS-B", 
  control = list(fnscale = -1, trace = 6))

@@

```{r obesity_access_models}
tracts@data <- tracts@data %>%
  mutate(
    access_ls = calculate_park_logsums(log(distances), parks$log_size,
                                       betas = tweets_sdm_val$par),
    tweets_ls = calculate_park_logsums(log(distances), parks$log_size, parks$log_tweets,
                                       betas = tweets_sdm_val$par),
    # demean
    access_ls = access_ls - mean(access_ls),
    tweets_ls = tweets_ls - mean(tweets_ls)
  )
